\chapter{Acknowledgements}

I would like to express my deepest gratitude to my supervisor, \textbf{Prof. Neeldhara Misra}, for her guidance, encouragement, and invaluable feedback throughout the writing process of this thesis. I am also grateful to the members of my thesis committee, \textit{Prof. Indranath Sengupta}, \textit{Prof. Sanjay Amrutiya}, and \textit{Prof. Projesh Nath Choudhury}, for their insightful comments and suggestions.

I want to thank \textbf{Prof. Ashutosh Rai} from \textit{IIT Delhi} for his weekly lecture series on Stable Matching, which helped me tremendously in completing my thesis. His expertise and dedication were invaluable, and I am grateful for his support.
I would like to thank my colleagues at \textit{IIT Gandhinagar} for their support, especially \textit{Ms. Saraswati Nanoti}, \textit{Mr. Harshil Mittal}, and \textit{Mr. Anant Kumar}, who have helped me with understanding proofs wherever I stumbled upon and provided valuable insights into my research.

I am grateful to my family for their unwavering love and support, especially my parents, who have encouraged me to pursue my academic dreams and believed in me even when I doubted myself.

They say that behind every successful student is a group of friends who kept them sane, and I can't thank my squad enough for doing just that. They listened to me complain about endless readings and deadlines, celebrated my small victories, and always had a joke or two to lift my spirits. I don't know how I would have survived this journey without their friendship, and I feel lucky to have them in my life. Here's to more laughs, adventures, and academic triumphs together! And specially thanks to \textit{Rik Da} and \textit{Sohini Di}, who were there for me when nobody else was. Their unwavering support and presence lifted me up in moments of solitude and uncertainty. I am forever grateful for the memories we created together.
\newline

Thank you all for your contributions to my success.
\bigskip

\begin{flushright}   \textbf{ARGHA SARDAR}, 21510035 \\ \textit{IIT Gandhinagar} \\ April, 2023 \end{flushright}
